Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-03-15 analysis/paper/paper.Rmd
bibliography and templates

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

>>>>

---
title: "Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete"
author:
  - Dominic Pollard
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/world-archaeology.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---
